Technical Report

### 2018-05-22 fully-abstract-comp/ftlr-proof-cases.tex
Fixed some wrong assumptions in FTLR proof
Added a missing case
Add simple proofs for some minor lemmas.

\begin{lemma}[purePart is idempotent]
  For all $W$, $\mathit{purePart}( \purePart{W} ) = \purePart{W}$
  \label{lem:purePart-idempotent}
\end{lemma}
\begin{proof}
  Follows easily from the definition.
\end{proof}

@@

\item $\Phi_S' = \xjumpResult{c}{c}{\Phi_S}$
\item $\Phi_T' = \xjumpResult{c}{c}{\Phi_T}$

@@

>>>>

\begin{lemma}[purePart is duplicable]
  \label{lem:purePart-duplicable}
 For all $W$, we have that $W = W \oplus \purePart{W}$.
\end{lemma}
\begin{proof}
  Follows from the definition of $\purePart{}$ and $\oplus$.
\end{proof}

\begin{lemma}[purePart is idempotent]
  For all $W$, $\mathit{purePart}( \purePart{W} ) = \purePart{W}$ and $\purePart{W} = \purePart{W} \oplus \purePart{W}$.
  \label{lem:purePart-idempotent}
\end{lemma}
\begin{proof}
  The first part follows easily from the definition.
  The second statement follows from the first, together with Lemma~\ref{lem:purePart-duplicable}.
\end{proof}

\begin{lemma}[purePart is monotone]
  \label{lem:purePart-mono}
 For all $W'\future W$, we have that $\purePart{W'} \future \purePart{W}$.
\end{lemma}
\begin{proof}
  Follows easily from the definition of $\purePart{}$ and $\future$.
\end{proof}

\begin{lemma}[Increasing authority is the future]
  \label{lem:oplus-future}
  For all $W$, we have that:
  $W_1 \oplus W_2 \future W_1$
\end{lemma}
\begin{proof}
  Follows easily from the definitions.
\end{proof}

\begin{lemma}[Purity is a thing of the past]
  \label{lem:world-fut-purePart}
  For all $W$, we have that $W \future \purePart{W}$.
\end{lemma}
\begin{proof}
  Consequence of Lemmas~\ref{lem:purePart-duplicable}
  and~\ref{lem:oplus-future}.
\end{proof}

@@

\item $\Phi_S' = \Phi_S\updReg{\pcreg}{c}$
\item $\Phi_T' = \Phi_T\updReg{\pcreg}{c}$

@@

    \item (cca,seta2b) $w_1 = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma,\sigma'}$, $w_1' = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma,\sigma'}$, $\Phi_S(r_1) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma,\sigma'}$ and $\Phi_T(r_1) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma,\sigma'}$, $k = 1$

### 2018-05-22 fully-abstract-comp/technical-report.tex
Add simple proofs for some minor lemmas.

\begin{lemma}[purePart is idempotent]
  \label{lem:purePart-idempotemt}
  For all $W$, we have that $\purePart{W} = \purePart{W} \oplus \purePart{W}$ and $\purePart{W} = \purePart{}(\purePart{W})$.
\end{lemma}

@@

\begin{lemma}[Purity is a thing of the past]
  \label{lem:world-fut-purePart}
  For all $W$, we have that $W \future \purePart{W}$.
\end{lemma}
\begin{proof}
  Direct consequence of Lemmas~\ref{lem:purePart-duplicable}
  and~\ref{lem:oplus-future}.
\end{proof}

>>>>

\begin{lemma}[purePart is idempotent]
  \label{lem:purePart-idempotemt}
  For all $W$, we have that $\purePart{W} = \purePart{}(\purePart{W})$ and $\purePart{W} = \purePart{W} \oplus \purePart{W}$.
\end{lemma}

@@

\begin{lemma}[Purity is a thing of the past]
  \label{lem:world-fut-purePart}
  For all $W$, we have that $W \future \purePart{W}$.
\end{lemma}
